---
title: "Cronbach's Alpha (Internal Consistency)"
author: "Anita Restrepo"
date: "`r format(Sys.time(), '%b %d, %Y')`"
output: html_document
---
  
  
This is code for calculating the internal consistency of a questionnaire using Cronbach's alpha.    
  
```{r include = FALSE}
# ensures none of the code chunks are actually run (because non-functional
# code snippets will not allow for knitting)
knitr::opts_chunk$set(eval = FALSE)
```
  
Libraries required:  
```{r}
library(tidyverse)
library(ltm)
```


To calculate Cronbach's alpha you need to feed a dataframe into the `cronbach.alpha` function of the ltm package that contains the individual item-level responses for each subject (one subject per row). Any items that require it should be reverse-scored.  
```{r}
alpha <- example_dataframe %>%
  # select all the individual items of the questionnaire
  select(UCLA_1_rev:UCLA_20_rev, # items that had to be reverse-scored
         UCLA_2:UCLA_4, UCLA_7, UCLA_8, UCLA_11:UCLA_14, UCLA_17, UCLA_18) %>%
  # calculate cronbach's alpha in the sample
  cronbach.alpha(.)
# save the rounded alpha value as an R object to reference in Markdown when writing up
(alpha <- round(alpha$alpha, digits = 2))
```
  
See [this link](https://www.statology.org/cronbachs-alpha-in-r/) for a nice tutorial
  
  