---
title: "Regression Table"
author: "Anita Restrepo"
date: "`r format(Sys.time(), '%b %d, %Y')`"
output: html_document
---
  
  
Code for outputting a table with betas, SEs, and type-III Anova results for each predictor in a multilevel model.   
  
```{r include = FALSE}
# ensures none of the code chunks are actually run (because non-functional
# code snippets will not allow for knitting)
knitr::opts_chunk$set(eval = FALSE)
```
  
Libraries required:  
```{r}
library(tidyverse)
library(kableExtra)
```

  
The first part of the code makes a dataframe that has the desired columns and rows to make the table (so not the code for making the actual table).      
```{r}
sigs <- total_mod_chis %>%
  mutate(Predictor = c("Intercept", "Condition", "Cyberball Round",
                       "Loneliness", "Condition * Round",
                       "Condition * Loneliness", 
                       "Loneliness * Round", "Condition * Round * Loneliness")) %>%
  relocate(Predictor)
rownames(sigs) <- NULL
# insert blank rows for contrasts
sigs <- insertRows(sigs, c(3, 7, 9, 12), new = "")
## deal with bug in Berry package
sigs <- sigs[-c(13),]

betas <- total_mod_betas %>%
  mutate(Predictor = c("Intercept", "Condition", "", "Cyberball Round",
                       "Loneliness", "Condition * Round", "",
                       "Condition * Loneliness", "", 
                       "Loneliness * Round", "Condition * Round * Loneliness", ""),
         Contrast = c("", "Inclusion", "Neutral", "",
                       "", "Inclusion", "Neutral",
                       "Inclusion", "Neutral",
                       "", "Inclusion",
                       "Neutral")) %>%
  relocate(Predictor, Contrast)
rownames(betas) <- NULL

tab1 <- cbind(select(betas, -Predictor), select(sigs, -Predictor))
rownames(tab1) <- NULL

```
  
The second part of the code is for making the table itself. I pipe in the final dataframe I made above that has all the rows and columns the way I would want for them to appear in the table. 
  
```{r}
kable(tab1, col.names = c("Predictor", "$\\beta$", "SE", "$\\chi^2$", "Df", "p-value"), align = c("l", "c", "c", "c", "c",  "c")) %>% 
  kable_classic() %>%
  pack_rows(index = c("Intercept" = 1, "Condition" = 2, 
                      "Cyberball Round" = 1,
                       "Loneliness" = 1, "Condition * Round" = 2,
                       "Condition * Loneliness" = 2, 
                       "Loneliness * Round" = 1, 
                      "Condition * Round * Loneliness" = 2)) %>%
  footnote(general = "Loneliness is grand-mean centered. Reference category for Cyberball condition is exclusion. Higher scores on rejection questionnaires indicate greater feelings of rejection.")
```
  
Further reading: the [kableExtra package](https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html).
  
  
  
  